Current and future constraints on primordial magnetic fields

### 2015-11-04 pmf.tex
chang's para

>>>>

The density and stress perturbations introduced by PMFs give rise to the vorticity and gravitational waves. The CMB anisotropies created in this photon-baryon plasma inherit two characteristic properties, i.e., vector and tensor modes which can be determined by modified Boltzman equations involving sources from PMFs. The PMF filed is assumed to be Gaussian and its power spectrum is given by a power law $Ak^{n_s}$. Here $n_s$ is the spectral index of PMF and $A$ is its amplitude. The rms of the PMF energy can be quantified over a length 1\rm{Mpc} and $B_{\rm{1Mpc}}$ equivalently determines the PMF amplitude. The PMF stress anisotropies can be compensated by neutrinos if neutrinos decoupled too early so it is also important to consider when the PMF was generated and another parameter $\beta=\ln(a_{\nu}/a_{\rm{PMF}})$ is usually adopted.
